---
title: "R package"
author: "Jack Schwarz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(JackPackage)
```


# Introduction
Welcome to my R Package! I made this package over the course of my Fall 2020 Semester at The University of Oklahoma as part of my Statistics class with Dr. Wayne Stewart. 

I actually started with a different package, but I was doing things wrong and it was nasty, so I made this new one and will continue to use it going forward. 

This package, **JackPackage** (creatively named I know), contains three functions we have used in various labs, and one I made myself to help with ingesting data files. These functions are `mybin()`, `mycltu()`, `myci()`, and `myreadin()`.

All of these functions accomplish different things, and their documentation can be found either in the function documentation, or the package vignette.

# myreadin()

```{r first}
csvEx <- JackPackage::myreadin('EXAMPLECSV')
xlsEx <- JackPackage::myreadin('EXMAPLEXLS')
head(csvEx)
head(xlsEx)
```


# myci()

```{r second}
x = rnorm(30, mean=10, sd=12)
JackPackage::myci(x, conf=.90)
```


# mybin()

```{r third}
JackPackage::mybin(iter=1000, n=10, p=.7)
```


# mycltu()

```{r forth}
JackPackage::mycltu(25, 1000, 0, 5)
```

# The github repository

This is the address of my GITHUB repository:
<https://github.com/Jackschwarz58/OU-Math4753-Fall>

